---
title: "PRIMA-Panel Performance Report" 
date: "`r Sys.Date()`"
outputl: html_document
params:
  TTZ: NA
  TTF: NA
  table: NA
  minor: NA
  major: NA
  pre_histo: NA
  post_histo: NA
  combo_histo: NA
  gg_pre_bar: NA 
  gg_post_bar: NA
  gg_pre_pie: NA
  gg_post_pie: NA
  pre_sprec: NA
  post_sprec: NA
  error_input: NA
---

``` {r logo, echo=FALSE}

htmltools::img(src = knitr::image_uri("C:/Users/funkalexa/Documents/Code/QC-Tool/QC-Tool/www/logo.png"), 
               alt = 'logo', 
               style = 'float:left; padding:2px; width: 180px; height: 180px') # Added width and height as CSS


```


<br>
A <b>PRIMA</b>-Panel report has been generated. The report contains information about the pre-analytical composition of the cohort. It has generated graphs and tables for pre- and post-centrifugation delays. It applied these data to the established parameter models to estimate changes per processing delays for each metabolic parameter. 
<br>
<br>
Developed by [Alexander Funk](https://www.uniklinikum-dresden.de/de/das-klinikum/kliniken-polikliniken-institute/klinische-chemie-und-laboratoriumsmedizin/forschung/copy_of_EMS) at University Hospital Dresden. <br>
If you have used PRIMA-Reports in your research please cite our [publication.]()
<br>
<br>
<br>




---

# Meta Information

The processing delay (pre- and post-) are summarized in the following plots and tables. The SPREC has been calculated from the given processing delays. The plots give an overview of the distribution of processing delays as well as the categorization into the SPREC.


### SPREC Distribution Overview

``` {r dt_pre, echo=FALSE, warning=FALSE}
library(kableExtra)
kable(params$pre_sprec) %>% kable_styling(full_width = FALSE, position = "float_left")
kable(params$post_sprec) %>% kable_styling(full_width = FALSE, position = "left")

```

<br>

## 1D Histograms
Histograms show the distribution over the processing delays for the pre-centrifugation delays (left) and post-centrifugation delays (right).

``` {r histo, echo=FALSE, fig.show="hold",out.width="45%"}

params$pre_histo
params$post_histo

```

## 2D Hex Density Distribution
The 2D hex distribution plot combines destiny maps for pre-centrifugation as well as post-centrifugation delays to give a combined overview

``` {r hex, echo=FALSE, fig.show="hold",out.width="60%"}

params$combo_histo

```

## Treemap
The treemaps show the distribution of the samples according to the different SPREC Letters for the pre-centrifugation delays (left) and post-centrifugation delays (right)

``` {r tree, echo=FALSE, fig.show="hold",out.width="50%"}

params$gg_pre_pie
params$gg_post_pie

```

<br>

---


# Metabolite Predictions

The metabolite predictions were performed with the given pre-centrifugation and post-centrifguation delays.
The input error was considered to filter out parameters with error values above this threshold:
`r params$error_input` %



## Data Table
``` {r, echo=FALSE, warning=FALSE}
params$table
```
